---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/business-science/riingo.svg?branch=master)](https://travis-ci.org/business-science/riingo)
[![Coverage status](https://codecov.io/gh/business-science/riingo/branch/master/graph/badge.svg)](https://codecov.io/github/business-science/riingo?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/riingo)](https://cran.r-project.org/package=riingo)


# riingo

`riingo` allows you to access the Tiingo API for stock prices, cryptocurrencies,
and intraday feeds from the IEX (Investors Exchange). This can serve as an alternate
source of data to Yahoo Finance.

## Installation

Install the stable version from [CRAN](https://cran.r-project.org/) with:

``` r
install.packages("riingo")
```

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DavisVaughan/riingo")
```

## API Token

The first thing you must do is create an account and set an API token. 
I recommend using the two functions below to help create your account and find the token.

```{r, eval=FALSE}
riingo_browse_signup()
riingo_browse_token() # This requires that you are signed in on the site once you sign up
```

Once you have signed up and have an API token, I recommmend setting the token 
as an environment variable, `RIINGO_TOKEN` in an `.Renviron` file. The easiest
way to do this is with `usethis`.

```{r, eval=FALSE}
usethis::edit_r_environ()

# Then add a line in the environment file that looks like:
RIINGO_TOKEN = token_here
```

Do not put the token in quotes, and restart R after you have set it. 

See the documentation `?riingo_get_token()` for more information.

# Basic example

```{r, message=FALSE, warning=FALSE}
library(riingo)
```


Let's grab some data with `riingo`. The default parameters attempt to get 1 year's
worth of data.

```{r}
riingo_prices("AAPL")
```

But of course you can try and get as much as is available...

```{r}
riingo_prices("AAPL", start_date = "1950-01-01")
```

And multiple tickers work as well.

```{r}
riingo_prices(c("AAPL", "IBM"), start_date = "2001-01-01", end_date = "2005-01-01", resample_frequency = "monthly")
```


# Intraday data

You can get _limited_ intraday data with `riingo_iex_prices()`. This gives you
access to Tiingo's direct feed to the IEX.

```{r}
riingo_iex_prices("AAPL", resample_frequency = "1min")
```

See the documentation for all of the restrictions.

# Meta data

Meta data about each ticker is available through `riingo_meta()`.

```{r}
riingo_meta(c("AAPL", "QQQ"))
```

# Available tickers

You can check if a ticker is supported on Tiingo with `is_supported_ticker()` 
and you can get a `tibble` of all supported tickers with `supported_tickers()`

```{r}
is_supported_ticker("AAPL")

tickers <- supported_tickers()
tickers
```

# Quote data 

Another benefit of getting a feed from IEX is real time quote data. This includes
TOP (top of book) bid and ask prices, along with most recent sale prices.

It is normal for some fields to return `NA` when outside of trading hours.

```{r}
riingo_iex_quote(c("AAPL", "QQQ"))
```

# Crypto data

Cryptocurrency data can be accessed with `riingo_crypto_*()` functions. By default,
1 year's worth is pulled if available. Some tickers go back much further than others.

```{r}
riingo_crypto_prices(c("btcusd", "btceur"))
```

Intraday data is available as well. The intraday ranges are not well documented,
so it is a little hard to know what you can pull. From what I have discovered,
you can pull a few days at a time, with the max date of intraday data being about
~4 months back (When the date was April 5, 2018, I could pull intraday data back
to December 15, 2017, but only 5000 minutes at a time).

```{r}
riingo_crypto_prices("btcusd", start_date = Sys.Date() - 5, end_date = Sys.Date(), resample_frequency = "1min")
```

Also available are meta data with `riingo_crypto_meta()`, and TOP (top of book) 
quote data with `riingo_crypto_quote()`.

Lastly, you can extract raw (unaggregated) data feeds from multiple exchanges
by using the `raw = TRUE` argument in the price and quote crypto function.

# News Data

The Tiingo news feed can be accessed via the `riingo_news()` function. 

This function is only available for those who have a paid Power plan with Tiingo.

```{r}
riingo_news(ticker='AAPL', start_date = Sys.Date() - 5, end_date = Sys.Date(), limit=100)
```




# Related projects

* [tiingo-python](https://github.com/hydrosquall/tiingo-python) - A Python client for interacting with the Tiingo API.

* [quantmod](https://github.com/joshuaulrich/quantmod) - One of the data sources `quantmod` can pull from is Tiingo.
