---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# riingo

`riingo` allows you to access the Tiingo API for stock prices, cryptocurrencies,
and intraday feeds from the IEX (Investors Exchange). This can serve as an alternate
source of data to Yahoo Finance.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DavisVaughan/riingo")
```

## API Token

The first thing you must do is create an account and set an API token. 
I recommend using the two functions below to help create your account and find the token.

```{r, eval=FALSE}
riingo_browse_signup()
riingo_browse_token() # This requires that you are signed in on the site once you sign up
```

Once you have signed up and have an API token, I recommmend setting the token 
as an environment variable, `RIINGO_TOKEN` in an `.Renviron` file. The easiest
way to do this is with `usethis`.

```{r, eval=FALSE}
usethis::edit_r_environ()

# Then add a line in the environment file that looks like:
RIINGO_API = token_here
```

Do not put the token in quotes, and restart R after you have set it. 

See the documentation `?riingo_get_token()` for more information.

# Basic example

```{r, message=FALSE, warning=FALSE}
library(riingo)
```


Let's grab some data with `riingo`. The default parameters attempt to get 1 year's
worth of data.

```{r}
riingo_prices("AAPL")
```

But of course you can try and get as much as is available...

```{r}
riingo_prices("AAPL", start_date = "1950-01-01")
```

And multiple tickers work as well.

```{r}
riingo_prices(c("AAPL", "IBM"), start_date = "2001-01-01", end_date = "2005-01-01", resample_frequency = "monthly")
```


# Intraday data

You can get _limited_ intraday data with `riingo_prices_iex()`. This gives you
access to Tiingo's direct feed to the IEX.

```{r}
riingo_prices_iex("AAPL", resample_frequency = "1min")
```

See the documentation for all of the restrictions.

# Meta data

Meta data about each ticker is available through `riingo_meta()`.

```{r}
riingo_meta(c("AAPL", "QQQ"))
```

# Available tickers

You can check if a ticker is supported on Tiingo with `is_supported_ticker()` 
and you can get a `tibble` of all supported tickers with `supported_tickers()`

```{r}
is_supported_ticker("AAPL")

tickers <- supported_tickers()
tickers
```

# Quote data 

Another benefit of getting a feed from IEX is real time quote data. This includes
TOP (top of book) bid and ask prices, along with most recent sale prices.

It is normal for some fields to return `NA` when outside of trading hours.

```{r}
riingo_quote_iex(c("AAPL", "QQQ"))
```

